Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-04-14 Paper.tex
Constraints, explanations,
started solution tables, have not finished

The total revenue from all products produced and sold, less the cost of manufacture and inventory, is represented in this function.  While designed for a two-period optimization, the base function can be easily expanded to accomodate for more periods of production and sales.
%superscript for plant, sub for product and period??
\subsection{Constraints}
In construction of this model, the following constraints were constructed within the parameters set forth by the problem:
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq L_{i}
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq L_{i}
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq P_{i}
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq P_{i}
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq A
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq A
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} + e \leq G_{1} for i = g, y, z
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq G_{2} + e  for i = g, y, z
\end{equation}
\begin{equation}
QQQQ \leq x_{i,1} \leq S_{1} %What is a good variable for the constants for sales bounds
\end{equation}
\begin{equation}
QQQQ \leq x_{i,2} + x_{i,3} \leq S_{2}
\end{equation}
\begin{equation}
x_{i,j} \geq 0
\end{equation}

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Coding}
%Maybe insert a page of pseudocode here???????
Code
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts 
\section{Solution}
Explain results, compare to linear relaxation of the problem
\par
maybe insert a section with a graph or chart to visualize production
\section{Further Analysis}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.  EFFICIENCY
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{9}
\bibitem{bulger88}

>>>>

The total revenue from all products produced and sold, less the cost of manufacture and inventory, is represented in this function.  While designed for a two-period optimization, the base function can be easily expanded to accomodate for more periods of production and sales.
%superscript for plant, sub for product and period??
\subsection{Constraints}
In construction of this model, the following constraints were constructed within the parameters set forth by the problem:
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq L_{1} %Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq L_{2} % Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq P_{1} %packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq P_{2}%packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} + e \leq G_{1},  i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq G_{2} + e, i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq U_{1} , i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq U_{2},  i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
Min_{1} \leq x_{i,1} \leq Max_{1} %What is a good variable for the constants for sales bounds
\end{equation}
\begin{equation}
Min_{2} \leq x_{i,2} + x_{i,3} \leq Max_{2}
\end{equation}
\begin{equation}
x_{i,j} \geq 0, integer %how to best put this into math speak
\end{equation}
\begin{equation}
e \geq 0
\end{equation}

Constraints 1-4 represent the labor and packing limitations by plant with cost by product.  The first month's costs include the items manufactured and sold that month, as well as the items manufactured 
for carryover into the second month.  Constraints 5-8 represent the global constraints in this problem:  advertising budget and graphite stock.  The advertising budget is a fixed amount for each month, with no carryover. The 
graphite stock has a consistent amount per month as well, but excess from the first month can be carried over into the next month.  This carryover amount is represented by \textit{e}.  Constraints 9 \& 10 represent the unique assembly time 
for the sets of clubs, again varying by plant location. 
\par
The final constraints (11-14) represent variable bounds.  Constraint 11 ensures that all items produced and sold in period 1 are within the minimum and maximum demand.  Similarly, inequality 12 ensures that the sum of items produced in period 2 and items carryed over to 
period 2 are within that month's demand bounds.  Constraints 13 \& 14 further bound all items to be non-negative.

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Coding}
%Maybe insert a page of pseudocode here???????
Code
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts are an added constraint along a hyperplane to a vertex.  They are 
commonly implemented in most commercial integer programming solvers as an initial heuristic.  In optimization software implementations, these cuts tend to be accurate overall and invalid cuts are rarely made \cite{gomory}.
\section{Solution}
The model was successfully optimized to the same solution over several runs, yielding the following optimal solution with constraints as laid out in the original problem above:
\begin{table}
\begin{tabular}{ l c c c }
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\

Steel Shafts & 0 & 0 & 251 \\
Graphite Shafts & 100 & 2000 & 0 \\
Iron Heads & 200 & 0 & 200 \\
Metal Wood Heads & 35 & 1 & 30 \\
Titanium Insert Wood Heads & 2000 & 1299 & 701 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 35 & 84\\
\end{tabular}
\caption{Optimal Chandler Production}
\end{table}

\begin{tabular}{ c c c c }

\end{tabular}
%\caption*{Optimal Chandler Production}

\begin{tabular}{ c c c c }

\end{tabular}
%\caption*{Optimal Chandler Production}
\section{Further Analysis}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.  EFFICIENCY
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{9}
\bibitem{gomory}
G\'{e}rard Cornu\'{e}jols, Fran\c{c}ois Margot, \& Giacomo Nannicini. (2013). On the safety of Gomory cut generators. 
\textit{Mathematical Programming Computation, 5}(4), pp. 345-395.
